Survey.jl - An Efficient Framework for Analysing Complex Surveys

### 2024-09-15 paper/header.tex
Change proceedings year

\author[1]{Ayush Patnaik}
\affil[1]{XKDR Forum}

\author[2]{Nadia Enhaili}
\affil[2]{Simon Fraser University}

@@

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Ayush Patnaik},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}

>>>>

\author[1]{Ayush Patnaik}
\author[2]{Nadia Enhaili}
\author[3]{Siddhant Chaudhary}
\author[1]{Shikhar Mishra}
\author[4]{Iulia Dumitru}
\affil[1]{XKDR Forum}
\affil[2]{Simon Fraser University}
\affil[3]{Chennai Mathematical Institute}
\affil[4]{Politehnica University of Bucharest}

@@

\hypersetup{
pdftitle = {Survey.jl - An Efficient Framework for Analysing Complex Surveys},
pdfsubject = {JuliaCon 2024 Proceedings},
pdfauthor = {Ayush Patnaik, Nadia Enhaili, Siddhant Chaudhary, Shikhar Mishra, Iulia Dumitru},
pdfkeywords = {Julia, Survey, Statistics, Sampling},
}
